Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli

### 2023-12-29 manuscript_draft.Rmd
final final final v 4

  - name: Yangyang Yu
    email: yyu44@stevens.edu

@@

    affiliation: '6,27'

@@

  - name: Bastian Jaeger
    affiliation: '14'
    email: B.Jaeger@tilburguniversity.edu

@@

    affiliation: '15,28'

@@

@@

  - name: Jordan Suchow
    email: jsuchow@stevens.edu

@@

    affiliation: '19'

@@

    affiliation: '20,29'

@@

@@

    affiliation: '26'

@@

affiliation:
  - id: '1'
    institution: Analytics, Harrisburg University of Science and Technology
  - id: '2'
    institution: Department of Vision Sciences, University of Leicester
  - id: '3'
    institution: Department of Psychology, Princeton University
  - id: '4'
    institution: Illumin Analytics
  - id: '5'
    institution: Stevens Institute of Technology
  - id: '6'
    institution: Department of Neuroscience, University of Padova
  - id: '7'
    institution: Methodology and Statistics Unit, Institute of Psychology, Leiden
      University
  - id: '8'
    institution: Department of Developmental and Social Psychology, University of
      Padova
  - id: '9'
    institution: University of Leuven
  - id: '10'
    institution: Applied Memory Research Laboratory, Institute of Psychology, Jagiellonian
      University
  - id: '11'
    institution: Franklin and Marshall College
  - id: '12'
    institution: ETH Zürich
  - id: '13'
    institution: Department of Media and Communication, City University of Hong Kong
  - id: '14'
    institution: Tilburg University
  - id: '15'
    institution: Department of Psychology, University of Rochester
  - id: '16'
    institution: School of Psychology, The University of Queensland
  - id: '17'
    institution: Department of Psychology and Psychotherapy, Witten/Herdecke University
  - id: '18'
    institution: Programa de Investigación Asociativa (PIA) en Ciencias Cognitivas,
      Centro de Investigación en Ciencias Cognitivas (CICC), Facultad de Psicología,
      Universidad de Talca
  - id: '19'
    institution: University of Oslo
  - id: '20'
    institution: Massachusetts General Hospital
  - id: '21'
    institution: IRCCS San Camillo Hospital
  - id: '22'
    institution: Ashland University
  - id: '23'
    institution: Bournemouth University
  - id: '24'
    institution: University of Padova
  - id: '25'
    institution: California State University East Bay
  - id: '26'
    institution: University of Alabama
  - id: '27'
    institution: Padova Neuroscience Center, University of Padova
  - id: '28'
    institution: "Children's Institute Inc."
  - id: '29'
    institution: Harvard Medical School

@@

```{r setup, include = FALSE, echo = FALSE}
set.seed(895893)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
library(nlme)
library(MuMIn)
library(pwr)
library(latex2exp)
```

@@

```{r con-sample, include = F, echo = F}
# sequence of sample sizes to try
nsim <- 500
samplesize_values <- seq(20, 300, 5)
# create a blank table for us to save the values in 
sim_table <- matrix(NA, 
          nrow = length(samplesize_values)*nsim, 
          ncol = length(unique(con_use$Word)))
# make it a data frame
sim_table <- as.data.frame(sim_table)
# add a place for sample size values 
sim_table$sample_size <- NA

@@

```{r elp-sample, include = F, echo = F}
# sequence of sample sizes to try
nsim <- 500
samplesize_values <- seq(20, 300, 5)
# create a blank table for us to save the values in 
sim_table <- matrix(NA, 
          nrow = length(samplesize_values)*nsim, 
          ncol = length(unique(elp_use$Stimulus)))
# make it a data frame
sim_table <- as.data.frame(sim_table)
# add a place for sample size values 
sim_table$sample_size <- NA

@@

apa_table(results_table_example, 
          caption = "Sample Size Estimates by Decile for Example Study",
          note = "C = Concreteness rating, L = Lexical Decision Response Latencies. Estimates are based on meeting at least the minimum percent of items (e.g., 80%) but may be estimated over that amount (e.g., 82.5%). SE columns represent the standard error value cutoff for each decile, while 80/85/90/95 percent columns represent the sample size needed to have that percent of items below the SE cutoff. For example, 100 participants are required to ensure at least 95% of concreteness items SE are below the 10 percent decile SE cutoff, and 175 participants are necessary for the lexical decision SE to be below its 10 percent decile cutoff.")
```

>>>>

@@

    affiliation: '6,26'

@@

@@

    affiliation: '14,27'

@@

    affiliation: '15'

@@

@@

@@

    affiliation: '19,28'

@@

    affiliation: '20'

@@

@@

affiliation:
  - id: '1'
    institution: Analytics, Harrisburg University of Science and Technology
  - id: '2'
    institution: Department of Vision Sciences, University of Leicester
  - id: '3'
    institution: Department of Psychology, Princeton University
  - id: '4'
    institution: Illumin Analytics
  - id: '5'
    institution: Stevens Institute of Technology
  - id: '6'
    institution: Department of Neuroscience, University of Padova
  - id: '7'
    institution: Methodology and Statistics Unit, Institute of Psychology, Leiden
      University
  - id: '8'
    institution: Department of Developmental and Social Psychology, University of
      Padova
  - id: '9'
    institution: University of Leuven
  - id: '10'
    institution: Applied Memory Research Laboratory, Institute of Psychology, Jagiellonian
      University
  - id: '11'
    institution: Franklin and Marshall College
  - id: '12'
    institution: ETH Zürich
  - id: '13'
    institution: Department of Media and Communication, City University of Hong Kong
  - id: '14'
    institution: Department of Psychology, University of Rochester
  - id: '15'
    institution: School of Psychology, The University of Queensland
  - id: '16'
    institution: Department of Psychology and Psychotherapy, Witten/Herdecke University
  - id: '17'
    institution: Programa de Investigación Asociativa (PIA) en Ciencias Cognitivas,
      Centro de Investigación en Ciencias Cognitivas (CICC), Facultad de Psicología,
      Universidad de Talca
  - id: '18'
    institution: University of Oslo
  - id: '19'
    institution: Massachusetts General Hospital
  - id: '20'
    institution: IRCCS San Camillo Hospital
  - id: '21'
    institution: Ashland University
  - id: '22'
    institution: Bournemouth University
  - id: '23'
    institution: University of Padova
  - id: '24'
    institution: California State University East Bay
  - id: '25'
    institution: University of Alabama
  - id: '26'
    institution: Padova Neuroscience Center, University of Padova
  - id: '27'
    institution: "Children's Institute Inc."
  - id: '28'
    institution: Harvard Medical School

@@

```{r setup, include = FALSE, echo = FALSE}
set.seed(895893)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
library(nlme)
library(MuMIn)
library(pwr)
library(latex2exp)
```

@@

```{r con-sample, include = F, echo = F}
# sequence of sample sizes to try
nsim <- 500
samplesize_values <- seq(20, 500, 5)
# create a blank table for us to save the values in 
sim_table <- matrix(NA, 
          nrow = length(samplesize_values)*nsim, 
          ncol = length(unique(con_use$Word)))
# make it a data frame
sim_table <- as.data.frame(sim_table)
# add a place for sample size values 
sim_table$sample_size <- NA

@@

```{r elp-sample, include = F, echo = F}
# sequence of sample sizes to try
nsim <- 500
samplesize_values <- seq(20, 500, 5)
# create a blank table for us to save the values in 
sim_table <- matrix(NA, 
          nrow = length(samplesize_values)*nsim, 
          ncol = length(unique(elp_use$Stimulus)))
# make it a data frame
sim_table <- as.data.frame(sim_table)
# add a place for sample size values 
sim_table$sample_size <- NA

@@

apa_table(results_table_example, 
          caption = "Sample Size Estimates by Decile for Example Study",
          note = "C = Concreteness rating, L = Lexical Decision Response Latencies. Estimates are based on meeting at least the minimum percent of items (e.g., 80%) but may be estimated over that amount (e.g., 82.5%). SE columns represent the standard error value cutoff for each decile, while 80/85/90/95 percent columns represent the sample size needed to have that percent of items below the SE cutoff. For example, 150 participants are required to ensure at least 95% of concreteness items SE are below the 10 percent decile SE cutoff, and 345 participants are necessary for the lexical decision SE to be below its 10 percent decile cutoff.")
```
